%
% ==> preamble
\input{../preamble.tex}

\title{Notes on Real Analysis}
% <==

\begin{document}
\maketitle
% ==> Real Numbers
\chapter{Real Numbers}
\section{Properties of Real Numbers}
% ==> properties
For now, let me just assume that the set $\N,\Z$ and $\Q$ 
are already exist. Just note that they're an 
\emph{``Order Field''}. The thing is, there must be some 
number system that is quite \emph{larger} than $\Q$, because
for example, there is no $q\in\Q$ such that $q^2=2$.

To extend from $\Q$, we're going to make up a new number 
system (kinda cheat a little bit, dun you think?) denoted 
by $\R$, which has the addition operation
$(+)$ and multiplication $(\cdot)$ such that for all $a,b\in\R$
\[a+b\in\R\quad\text{and}\quad ab:=a\cdot b\in\R.\]
Since we extended from $\Q$, this new set $\R$ is going to inherit all
the properties from $\Q$ listed below

\begin{enumerate}[label={\bfseries[A\arabic*]}]
  \item for any $a,b\in\R$, then $a+b=b+a$ and $ab=ba$.
  \item for any $a,b,c\in\R$, then $a+(b+c)=(a+b)+c$ and 
    $a(bc)=(ab)c$
  \item there is a number (\emph{indentity}) $\theta\in\R$ 
    and $\gamma\in\R$ such that 
    $a+\theta=a\gamma=a$  for all $a\in\R$.
  \item for any $a\in\R$, 
    \begin{itemize}
      \item there exist an \emph{additive inverse} $\alpha$ 
        such that $a+\alpha=\theta$.
      \item if $a\neq \theta$, there exist a 
        \emph{multiplicative inverse} $\beta$ such that 
        $a\beta=\gamma$.
    \end{itemize}
  \item for any $a,b,c\in\R$, then $a(b+c)=ab+ac$.
\end{enumerate}

Well because $\Q\subset\R$ (subspace), the indentity $\theta$ 
and $\gamma$ are the same of those in $\Q$, which we already
know they're simply the numbers $0,1$. 
Note also that, we must assume that $0\neq 1$.
\begin{theorem}
  For any $a,b,c\in\R$, the following holds
  \begin{itemize}
    \item the \emph{additive} and the \emph{multiplicative} 
      indentity are unique. 
      (later denoted them by $0$ and $1$ resp.)
    \item the addition and multiplicative inverses are
      unique. (later denoted them by $-a$ and $a\inv$ resp.)
    \item if $a+c=b+c\iff a=b$.
    \item $a\cdot 0=0,~-a=(-1)a$ and $-(-a)=a$.
    \item if $ab=0$ then $a=0$ or $b=0$.
  \end{itemize}
\end{theorem}
The above theorem is not that hard to prove. However, I promise 
to come back to this point to provide a full proof about it.

What now? The set $\R$ here behaves the same as $\Q$. 
How is it possible that $\R$ is bigger that $\Q$?
Let's find the condition that $\Q$ is lack of.

A long the way, we're introduced \emph{bounded sets.}
% <==
% ==> bounded
\begin{definition}[Maximum and Minimum]
  Let $S\subset\R$.
  \begin{itemize}
    \item if there exists $M\in S$ such that 
      $M\geq s$ for all $s\in S$, then $M$ is said to be the
      maximum of $S$ and is denoted by $\max S$.
    \item if there exists $m\in S$ such that 
      $m\leq s$ for all $s\in S$, then $m$ is said to be the
      minimum of $S$ and is denoted by $\min S$.
  \end{itemize}
\end{definition}
\begin{definition}[Bounded Sets]
  The set $S\subseteq\R$ is called
  \begin{itemize}
    \item \emph{bounded above} if $\exists M\in\R$ such that 
      $s\leq M$ for all $s\in S$.
    \item \emph{bounded below} if $\exists m\in\R$  such that
      $m\leq s$ for all $s\in S$.
    \item \emph{bounded} if it is both bounded below and above, 
      that is $\exists M>0$ such that $\abs{s}<M$ for all $s\in S$.
  \end{itemize}
\end{definition}
\begin{definition}[Upper and Lower bounds]
  Let $S\subseteq\R$ be a bounded set. We denote
  \begin{itemize}
    \item the set of all upper bounds of $S$ by 
      $\mathcal{U}(S)=\set{M\in\R}{M\geq s \text{ for all }s\in S}$
    \item the set of all lower bounds of $S$ by
      $\mathcal{L}(S)=\set{m\in\R}{m\leq s\text{ for all }s\in S}$
  \end{itemize}
\end{definition}
\begin{definition}[Infimum and Supremum]
  Let $S$ be a bounded set. If
  \begin{itemize}
    \item the set $\mathcal{U}(S)$ has a minimum $\alpha$, then the set
      $S$ is said to have a \emph{supremum}, that is
      $\sup S:=\alpha$.
    \item the set $\mathcal{L}(S)$ has a maximum $\beta$,
      then the set $S$ is said to have an \emph{infimum}, that is
      $\inf S:=\beta$.
  \end{itemize}
\end{definition}
% <== 
% ==> AoC
\begin{axiom}[Axiom of Completeness]
  Every non-empty subset of $\R$ that is bounded above 
  has a supremum.
\end{axiom}
% <==
% <==


% ==> abs convergence
\newpage
\begin{example}
  The function $f(x)=2x+1$ converges over $\R$.
  Note that $\forall x\in\R$
  \[\abs{f(x)-f(x_0)}=2\abs{x-x_0}\]
  therefore we can choose $\delta=\frac{\epsilon}{2}$
  which does not depend on the choise of $x_0$.
\end{example}
\begin{example}
  The function $f(x)=x^2$ converges over $\R$.
  Note that $\forall x_0\in\R$
  \[\abs{f(x)-f(x_0)}=\abs{x^2-x_0^2}=\abs{x-x_0}\cdot\abs{x+x_0}\]
  Suppose that $\abs{x-x_0}<1$ and hence 
  \[\abs{x+x_0}<\abs{x-x_0}+\abs{2x_0}<1+\abs{2x_0}\]
  So we can choose $\delta=\min\left\{1,\frac{\epsilon}{1+2\abs{x_0}}\right\}•$
  which depends on the choise of $x_0$.
\end{example}
\begin{definition}[Absolutely Convergent]
  The function $f:\mathcal{D}\to\R$ is said to be \emph{Absolutely Convergent}
  iff for each $\epsilon>0$ there exists $\delta>0$ such 
  that $\forall x,y\in\mathcal{D}$ 
  \[\abs{x-x_0}<\delta\implies\abs{f(x)-f(y)}<\epsilon.\]
\end{definition}
% <==



\end{document}
